\large{\bf Normality and large effect loci in quantitative genetics }

### 2023-07-04 writeup.tex
not too many rows plz

We next compared two situations of stabilizing selection, motivated by the results above
\comment{TODO: refer to where?}:
(1) the effect size distribution was Gaussian with mean zero and standard deviation $\sigma_g$,
and $f(z) = e^{\alpha z^2}$; and
(2) the effect size distribution was Cauchy, centered at zero and with width $\delta - \gamma$
and $f(z) = (\delta/\gamma) (\gamma + z^2) / (\delta + z^2)$.
Figure XXX shows the resulting distributions of segregation noise:
i.e., the distribution of child phenotype minus average of parents' phenotypes,
across all offspring following burn-in.

>>>>

We next compared two situations of stabilizing selection, motivated by the results above
\comment{TODO: refer to where?}:
(1) the effect size distribution was Gaussian with mean zero and standard deviation $\sigma_g$,
and $f(z) = e^{\alpha z^2}$; and
(2) the effect size distribution was Cauchy, centered at zero and with width $\delta - \gamma$
and $f(z) = (\delta/\gamma) (\gamma + z^2) / (\delta + z^2)$.
Figures~\ref{fig:sel_trait_distrns} and~\ref{fig:sel_seg_noise}
show that the picture is largely unchanged by stabilizing selection
except that, unsurprisingly, the median trait is no longer constrained to wander
(but still shows substantially larger fluctuations under the Cauchy model).

\begin{figure}
    \begin{center}
        \includegraphics{sims/selected_seg_noise_small}
    \end{center}
    \caption{
        As in Figure~\ref{fig:seg_noise},
        except computed using only mutations with absolute value effect size less than 0.1.
        \label{fig:seg_noise_small}
    }
\end{figure}

However, as suggested above,
the two models look much more similar when considering only alleles of small effect.
Figure~\ref{fig:seg_noise_small} shows that ``midparent value''
and ``segregation noise'' computed using only mutations with effect size less than 0.2
(excluding less than 1\% of mutations)
are quite close to independent.
The result does not depend strongly on the cutoff chosen,
and are similar even if less 0.1\% of mutations are excluded.
